Testing Stacked Bar Charts: viewers' perceptual accuracy in surveys

### 2023-10-16 revisions-round1/response-to-reviewers.qmd

-   **There are a couple of assumptions that assume certain factors (order of question, rounds) are negligible to the outcome. While I think this is reasonable, for a higher confidence in results it might be a good idea to test all visual stimulus within each round and block (if it is hard to be individually randomised) so that some participants get different question order.**

-   Major comments

    -   **The title, abstract and conclusion suggests a wider context but the content is actually more limited in scope. I suggest changing the title to emphasise the main points in the article: 1) nationally representative sample and 2) testing stacked barplots. I think statements like "Our study results provide actionable insights that data visualization practitioners can utilize in the design of data visualizations." extrapolates too much. It should be more specific in that the actionable insights is *for stacked barplots* and also write concretely what the recommendation is (i.e., vertical display, align groups that most important to compare, etc.).**
        -   *We have updated the statement in the conclusions per a specific recommendation in the minor comments. In addition, we have updated the paper title and some of the language in the abstract to reflect that the scope is limited to testing stacked bar charts.* **We will also update the recommendation language to be more concrete**

    -   Do the authors have recommendations for (non-representative) visualisation perception surveys given their experience on nationally representative sample? E.g. given that the surveys conducted via Mturks etc are biased toward highly educated young males and authors found differences between the income group, what do these non-representative survey inform us?
        -   *We have added the following text to our conclusions to address this point: "If studies using non-representative or crowd-sourced samples find non-significant results when studying elements of design, those results may not actually be non-significant for other populations, particularly lower education or lower income populations. Researchers should not disregard non-significant findings in those survey studies but rather ask whether the lack of significance would hold across population subgroups."*

### 2023-10-16 SDSS-2023/testing-charts-accuracy.qmd
language addition in conclusion per reviewer 2

Perhaps most salient among our results are the patterns in response behavior across demographic groups.
The large size of our sample, paired with the probability-based survey panel approach, afford us the ability to dive into response patterns among demographics across tasks and identify significant differences among them.
In particular, the differences across educational attainment groups and income groups underscore the importance of utilizing a representative population when testing perception; prior results in this area may be absorbing bias in responses due to the larger representation of individuals with higher education levels among those study respondents.

>>>>

Perhaps most salient among our results are the patterns in response behavior across demographic groups.
The large size of our sample, paired with the probability-based survey panel approach, afford us the ability to dive into response patterns among demographics across tasks and identify significant differences among them.
In particular, the differences across educational attainment groups and income groups underscore the importance of utilizing a representative population when testing perception; prior results in this area may be absorbing bias in responses due to the larger representation of individuals with higher education levels among those study respondents. If studies using non-representative or crowd-sourced samples find non-significant results when studying elements of design, those results may not actually be non-significant for other populations, particularly lower education or lower income populations. Researchers should not disregard non-significant findings in those survey studies but rather ask whether the lack of significance would hold across population subgroups.
